Tampering Detection In Low-Power Smart Cameras

### 2015-05-26 paper.tex
edits in Section 3

@@

When at time $\tau^*$ an external disturbance introduces \emph{blur/defocus}, the image $y_t$ is degraded by a spatially variant blur operator, and $z_t$ becomes
\begin{equation}
\label{eq:model_defocus}
\mathcal{D}_t[y_t](x) = \int_{\mathcal{X}}y(s)h_t(x,s)ds\, + \eta_t(x) \quad \forall x \in X, t \geq \tau^*
\end{equation}
%where  $\mathcal{B}_t$ corresponds to a linear operator
%\begin{equation}
%\label{eq:blur}
%\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(x,s)ds\,,
%\end{equation}
where $h_t(x,\cdot) > 0$ is the point-spread function at pixel $x \in X$.
%\begin{equation}
%\label{eq:blur_convolution}
%\mathcal{B}[y](x) = \int_{\mathcal{X}}y(s)h(s-x)ds,
%\end{equation}
%
%\begin{equation}
%\label{eq:blur_multi}
%z_t(x)=\mathcal{D}_t[y_t](x) = \mathcal{B}_t[y_t](x) + \eta(x), \qquad x \in \mathcal{X}.
%\end{equation}
A \emph{camera displacement} at frame $\tau^*$ is instead modeled as 
\begin{equation}
\label{eq:model_displacement}
z_t(x)  = \left\{ \begin{array}{rcl}
y_t(x) + \eta(x) & \mbox{per} & t < T^* \\
w_t(x) + \eta(x) & \mbox{per} & t \geqslant T^*
\end{array}\right. ,
\end{equation}
where $w_t$ relates to a different viewpoint and/or camera orientation than $y_t$.

The proposed tampering-detection algorithm analyzes a sequence of frames $\{z_t\}_t$ to detect time $\tau^*$ when any tampering like \eqref{eq:model_defocus} or \eqref{eq:model_displacement} occurs.

%Per $t<T^*$ abbiamo che i frame vengono acquisiti in condizioni di funzionamento normale:
%\[ z_t(x)=y_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t=1,\dots , T^*-1. \] 
%All'istante di tempo $t = T^*$ avviene un evento di tampering, il quale compromette i frame per $t\geq T^*$.  
%In particolare, nel caso di una sfocatura avremo
%\[ z_t = \mathcal{B}_t[y_t](x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*,\]
%mentre nel caso di uno spostamento della camera avremo
%\[ z_t = w_t(x) + \eta(x), \forall x \in \mathcal{X} \mbox{, per } t \geq T^*. \]

@@

The proposed tampering-detection algorithm is illustrated in Algorithm \ref{alg:DISPL}, and relies on two indicators that are very simple to compute: the average intensity (also referred to as \emph{luma} and denoted by $l$) and the average norm of the gradient (denoted by $g$). As anticipated in Section \ref{sec:introduction}, during algorithm configuration we perform a preliminary segmentation of the scene, yielding $\{R_k\}, k = 1,\dots,K,$  $R_k \subset \mathcal{X}$, a collection of disjoint subsets ($R_i  \cap R_j = \emptyset, \forall i \neq j$), and we compute and monitor the luma indicator separately on each $R_k$. Details about the scene segmentation algorithm used are reported in Section \ref{subsec:Segmentation}.

Luma is computed separately on each of the $K$ image regions in each frame $z_t$
\begin{equation}\label{eq:lumaRegions}
l_k(t) =\frac{1}{\#R_k} \sum_{R_k} z_t(x), \ \ k = 1, \dots, K\,,
\end{equation}
while the gradient norm is
\begin{equation}
\label{eq:normaGradiente}
g(t) = \sum_X \left (\sqrt{\left(z_t \circledast f_h\right)^2(x) + \left(z_t \circledast f_v\right)^2(x)}\right),
\end{equation}
where $f_h$ and $f_h$ are horizontal and vertical derivative filters, respectively, $\#(\cdot)$ indicates the cardinality of a set and $\circledast$ the 2d convolution.

Tampering attacks are analyzed by determining whether indicators computed from each incoming frame yield an outlier. Since these indicator are univariate, we simply

Monitoring these indicators is challenging because they are highly correlated overtime and and it is not possible to 
%\partial l^k(t) & =& l^k(t)-l^k(t-1)

\begin{algorithm}[t]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{R_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}

\subsection{Scene Segmentation}\label{subsec:Segmentation}
Consideriamo la sequenza $\{z_t\}$ di frame acquisiti dalla camera, con $t=1,\dots,T_{c}$.
Per ciascun pixel $x\in\mathcal{X}$ calcoliamo un vettore $\textbf{d}(x)$ di $5$ elementi
\begin{equation}
\label{eq:featureVector}
\textbf{d}(x)=\left[r(x);c(x);\mu_{\nabla}(x);\sigma_{\nabla}(x);\bar{z}(x)\right], \textbf{d}(x) \in \mathbb{R}^5
\end{equation}
dove:
\begin{itemize}
	\item $r(x)$ rappresenta il numero di riga del pixel $x$.
	\item $c(x)$ rappresenta il numero di colonna del pixel $x$.
	\item $\mu_{\nabla}(x)$ rappresenta il valore del gradiente nel pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneGrad}
	\mu_{\nabla}(x) = \frac{\sum_{t=1}^{T_c}(\|\nabla z_t\|_2^2 \circledast f)(x)}{T_c},
	\end{equation}
	dove abbiamo indicato con $\|\nabla z_t\|_2^2$ la norma del gradiente per l'immagine $z_t$, definita in \eqref{eq:normaGradiente}, e con $f$ il filtro gaussiano discreto derivato dal campionamento di \eqref{eq:gaussian}.
	\item $\sigma_{\nabla}(x)$ rappresenta la deviazione standard nel tempo del gradiente nel pixel $x$:
	\begin{equation}
	\label{eq:segmentazioneVar}
	\sigma_{\nabla}(x)=\sqrt{\frac{1}{T_c - 1}\sum_{t=1}^{T_c}\left(\left(\|\nabla z_t\|_2^2 \circledast f\right)(x)-\mu_{\nabla}(x)\right)^2}.
	\end{equation}
	\item $\bar{z}(x)$ rappresenta il valore della luma del pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneLuma}
	\bar{z}(x)=\frac{\sum_{t=1}^{T_c}( z_t \circledast f)(x)}{T_c}.
	\end{equation}
\end{itemize}
%
%
%
\subsection{Indicators}\label{subsec:Indicators}

\begin{equation}
\label{eq:gradientRegions}
\begin{array}{ccc}
g^k(t)&  = & \mathcal{G}^k[z_t] = \frac{\sum_{R_k}\| \nabla z_t(x) \| _2^2 }{|{R_k}|}\\
\partial g^k(t) & =& g^k(t)-g^k(t-1) 
\end{array},
\end{equation}

In particolare, per il calcolo delle derivate orizzontali  abbiamo utilizzato il seguente filtro $f_h$:
\[f_h = f \circledast \left[ \begin{array}{rcl}
1 & 0 & -1
\end{array}\right], \] 
mentre per il calcolo delle derivate verticali abbiamo utilizzato il seguente filtro $f_v$:
\[f_v = f \circledast \left[ \begin{array}{r}
1 \\ 0 \\ -1
\end{array}\right], \]
dove abbiamo indicato con $\circledast$ l'operatore di convoluzione.
Il filtro $f$, invece, \`e ottenuto tramite un campionamento della \textit{funzione gaussiana} $h$, con media $0$ e deviazione standard $\sigma$
\begin{equation}
\label{eq:gaussian}
h(i,j)=\frac{1}{2\pi\sigma^2}\exp\left(-\frac{i^2+j^2}{2\sigma^2}\right),
\end{equation}
e ponendo il valore massimo di questa funzione nel centro del filtro.
Con questi filtri \`e possibile calcolare la \textit{norma del gradiente} nel seguente modo:

Una volta calcolata la norma del gradiente \`e possibile farne la media come specificato in \eqref{eq:energyGradient}.
Il risultato finale \`e un indicatore \textit{scalare} per ciascun frame acquisito, che pu\`o essere monitorato per individuare eventi di sfocature. 
In particolare ci aspettiamo che l'evento di sfocatura provochi un abbattimento del valore di $g$.

@@

>>>>

%\newcommand{\gi}[1]{}
%\newcommand{\ad}[1]{}
%\newcommand{\cl}[1]{}

@@

When at time $\tau^*$ an external disturbance introduces \emph{blur/defocus}, the image $y_t$ is degraded by a spatially variant blur operator, and $z_t$ becomes
\begin{equation}
\label{eq:model_defocus}
\mathcal{D}_t[y_t](x) = \int_{\mathcal{X}}y(s)h_t(x,s)ds\, + \eta_t(x) \quad \forall x \in X, t \geq \tau^*
\end{equation}
where $h_t(x,\cdot) > 0$ is the point-spread function at pixel $x \in X$.

A \emph{camera displacement} at frame $\tau^*$ is instead modeled as 
\begin{equation}
\label{eq:model_displacement}
z_t(x)  = \left\{ \begin{array}{rcl}
y_t(x) + \eta(x) & \mbox{per} & t < T^* \\
w_t(x) + \eta(x) & \mbox{per} & t \geqslant T^*
\end{array}\right. ,
\end{equation}
where $w_t$ relates to a different viewpoint and/or camera orientation than $y_t$.

The proposed tampering-detection algorithm analyzes a sequence of frames $\{z_t\}_t$ to detect time $\tau^*$ when any tampering like \eqref{eq:model_defocus} or \eqref{eq:model_displacement} occurs. We require that the initial $T_0$ frames are without tampering and provided for training.

@@

Algorithm \ref{alg:DISPL} presents the proposed tampering detection, which relies on two indicators that are very simple to compute: the average intensity (also referred to as \emph{luma}, and denoted by $l$) and the average norm of the gradient (denoted by $g$). The former is meant to detect camera displacement, the latter camera defocus. As anticipated in Section \ref{sec:introduction}, during the initial configuration, the scene is segmented in $\{R_k\}, k = 1,\dots,K$ disjoint regions ($R_k \subset \mathcal{X}, R_i \cap R_j = \emptyset, \forall i \neq j$). Details about the employed segmentation algorithm are in Section \ref{subsec:Segmentation}.

In each frame $z_t$ the luma is separately computed in of the $K$ regions,
\begin{equation}\label{eq:lumaRegions}
l_k(t) =\frac{1}{\#R_k} \sum_{R_k} z_t(x), \ \ k = 1, \dots, K\,,
\end{equation}
while the average gradient norm is computed over the whole image
\begin{equation}
\label{eq:normaGradiente}
g(t) = \sum_X \left (\sqrt{\left(z_t \circledast f_h\right)^2(x) + \left(z_t \circledast f_v\right)^2(x)}\right),
\end{equation}
where $f_h$ and $f_h$ are the horizontal and vertical derivative filters, respectively, $\#(\cdot)$ indicates the cardinality of a set and $\circledast$ the 2d convolution.

As shown in Figure REFERENCE\_TODO.a), tampering results in outliers in the sequence of indicators. Detecting these outliers is not straightforward, since indicators heavily fluctuates in normal conditions because of short-term variations in the depicted scene or illumination changes. For outlier-detection purposes~\cite{Chandola2009}, it is more convenient to operate on sequences of independent and identically distributed (i.i.d.) values, where outliers can be detected by density-based methods or simply by confidence regions that is what we considered in our algorithm. Unfortunately, trends or deterministic variations in the indicator sequences are not easy to compensate because of unpredictable evolutions of the scene.

To obtain indicators that in normal conditions can be treated as i.i.d. realizations of a random variable we detrend~\cite{Gustafsson2000} the indicator sequence by performing temporal derivative
\begin{equation}\label{eq:detrending}
 \partial l_k(t) = l_k(t)-l_k(t-1),  \ \ k = 1, \dots, K\,,
\end{equation}
and we similarly define $\partial g(t)$. Detrended indicators are more suitable to be monitored by a confidence interval since, as shown in Figure REFERENCE\_TODO.b). However, a tampering yielding permanent changes in the indicators, as those in Figure REFERENCE\_TODO.a results in a single outlier in the detrended indicator~\eqref{eq:detrending}.

\begin{algorithm}[t]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\} k=1,\dots,K$ \\
	\textbf{Configuration}:\\
	\lnl{DISPL-Tr1} Compute $\partial l_k(t)$ and $\partial g(t), t = 1, \cdots, T_o$\\ 
	\lnl{DISPL-Tr7} Compute $\sigma_{l_k}$ and $\sigma_{g}$, the standard deviations of $\partial l_k$ and $\partial g$.\\

	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o} + 1,\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$, set $n_l =0$
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $\partial l_k(t)$\\
			\lnl{DISPL-Test6} \If{$\partial l_k(t) < -\gamma \sigma_{l_k} \vee \partial l_k(t) > \gamma \sigma_{l_k} $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} tampering (probably displacement or occlusion) has occurred in $z_t$ \\
		}
		\lnl{DISPL-Test10} Compute $\partial g(t)$\\
		\lnl{DISPL-Test11} \If{$\partial g(t) < -\gamma \sigma_{g} \vee \partial l(t) > \gamma \sigma_{g} $}{
				\lnl{DISPL-Test9} tampering (probably out-of-focus) has occurred in $z_t$ \\
								}

	}   
	\caption{The Proposed Tampering-Detection Algorithm}
	\label{alg:DISPL}
\end{algorithm}

\subsection{Scene Segmentation}\label{subsec:Segmentation}
Consideriamo la sequenza $\{z_t\}$ di frame acquisiti dalla camera, con $t=1,\dots,T_{c}$.
Per ciascun pixel $x\in\mathcal{X}$ calcoliamo un vettore $\textbf{d}(x)$ di $5$ elementi
\begin{equation}
\label{eq:featureVector}
\textbf{d}(x)=\left[r(x);c(x);\mu_{\nabla}(x);\sigma_{\nabla}(x);\bar{z}(x)\right], \textbf{d}(x) \in \mathbb{R}^5
\end{equation}
dove:
\begin{itemize}
	\item $r(x)$ rappresenta il numero di riga del pixel $x$.
	\item $c(x)$ rappresenta il numero di colonna del pixel $x$.
	\item $\mu_{\nabla}(x)$ rappresenta il valore del gradiente nel pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneGrad}
	\mu_{\nabla}(x) = \frac{\sum_{t=1}^{T_c}(\|\nabla z_t\|_2^2 \circledast f)(x)}{T_c},
	\end{equation}
	dove abbiamo indicato con $\|\nabla z_t\|_2^2$ la norma del gradiente per l'immagine $z_t$, definita in \eqref{eq:normaGradiente}, e con $f$ il filtro gaussiano discreto derivato dal campionamento di \eqref{eq:gaussian}.
	\item $\sigma_{\nabla}(x)$ rappresenta la deviazione standard nel tempo del gradiente nel pixel $x$:
	\begin{equation}
	\label{eq:segmentazioneVar}
	\sigma_{\nabla}(x)=\sqrt{\frac{1}{T_c - 1}\sum_{t=1}^{T_c}\left(\left(\|\nabla z_t\|_2^2 \circledast f\right)(x)-\mu_{\nabla}(x)\right)^2}.
	\end{equation}
	\item $\bar{z}(x)$ rappresenta il valore della luma del pixel $x$ mediato nel tempo:
	\begin{equation}
	\label{eq:segmentazioneLuma}
	\bar{z}(x)=\frac{\sum_{t=1}^{T_c}( z_t \circledast f)(x)}{T_c}.
	\end{equation}
\end{itemize}

@@

%
%
%
\subsection{Indicators}\label{subsec:Indicators}

%\begin{equation}
%\label{eq:gradientRegions}
%\begin{array}{ccc}
%g^k(t)&  = & \mathcal{G}^k[z_t] = \frac{\sum_{R_k}\| \nabla z_t(x) \| _2^2 }{|{R_k}|}\\
%\partial g^k(t) & =& g^k(t)-g^k(t-1) 
%\end{array},
%\end{equation}
%
%In particolare, per il calcolo delle derivate orizzontali  abbiamo utilizzato il seguente filtro $f_h$:
%\[f_h = f \circledast \left[ \begin{array}{rcl}
%1 & 0 & -1
%\end{array}\right], \] 
%mentre per il calcolo delle derivate verticali abbiamo utilizzato il seguente filtro $f_v$:
%\[f_v = f \circledast \left[ \begin{array}{r}
%1 \\ 0 \\ -1
%\end{array}\right], \]
%dove abbiamo indicato con $\circledast$ l'operatore di convoluzione.
%Il filtro $f$, invece, \`e ottenuto tramite un campionamento della \textit{funzione gaussiana} $h$, con media $0$ e deviazione standard $\sigma$
%\begin{equation}
%\label{eq:gaussian}
%h(i,j)=\frac{1}{2\pi\sigma^2}\exp\left(-\frac{i^2+j^2}{2\sigma^2}\right),
%\end{equation}
%e ponendo il valore massimo di questa funzione nel centro del filtro.
%Con questi filtri \`e possibile calcolare la \textit{norma del gradiente} nel seguente modo:
%
%Una volta calcolata la norma del gradiente \`e possibile farne la media come specificato in \eqref{eq:energyGradient}.
%Il risultato finale \`e un indicatore \textit{scalare} per ciascun frame acquisito, che pu\`o essere monitorato per individuare eventi di sfocature. 
%In particolare ci aspettiamo che l'evento di sfocatura provochi un abbattimento del valore di $g$.
